ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura Gati).}

### 2018-06-29 Latex/Draft_Summer2018/Summer2018.tex
more writing on robustness checks

Our simples identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment. We justify these assumptions with both empirical and theoretical argument. First of all, using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter. Thus, since the share of this sector accounts for a negligible part in the whole economy, we assume that an ICT shock is orthogonal to current TFP. In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy. As a result, we expect an ICT shock to have a maximal impact effect on ICT investment.

@@

Appendix \ref{section:mainSetResults} shows the estimated impulse responses of System \ref{eq:mainSpecification} to the identified ICT shock. The shaded gray areas are the $90$\% and $95$\% confidence bands from 2000 bias-corrected bootstrap procedure of \cite{kilian1998small}.

>>>>

Our simplest identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment. We justify these assumptions with both empirical and theoretical argument. First of all, using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter. Thus, since the share of this sector accounts for a negligible part in the whole economy, we assume that an ICT shock is orthogonal to current TFP. In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy. As a result, we expect an ICT shock to have a maximal impact effect on ICT investment.

@@

Appendix \ref{section:mainSetResults} shows the estimated impulse responses of System \ref{eq:mainSpecification} to the identified ICT shock. The shaded gray areas are the $90$\% and $95$\% confidence bands from 2000 bias-corrected bootstrap procedure of \cite{kilian1998small}. In particular, Figure \ref{fig:TFP_main} shows impulse response of TFP to an ICT shock. TFP takes around $4$ quarters before displaying a positive and significant effect and reaches its peak of $1.2$\% after $24$ quarters. In Figure \ref{fig:ICT_main}, real ICT investment has a large and positive impact response of almost $2$\% that gets even larger after a quarter. Then, it slowly starts to decay remaining significant for more than $40$ quarters. In Figures \ref{fig:GDP_main} and \ref{fig:C_main}, we present responses of real GDP and real consumption, respectively. Real GDP has a significant impact response of $0.3$\%, starts to increase and finally reaches its peak of almost $0.5$\% approximately at the same time of TFP. Similarly, real consumption has an impact effect of $0.2$\% with a delayed peak of $0.5$\%. Finally, in Figure \ref{fig:RP_main}, relative prices has a significant and negative impact response of $0.4$\% and remain persistently below their own steady state value for almost $9$ years.
